**The Mint Scale: A Fresh Validation of the Multimodal Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS**

### 2025-07-01 paper/manuscript.qmd
manuscript updated

The experiment included the following questionnaires.

**TODO: What about attention checks?**

@@

>>>>

The experiment included the following questionnaires. The procedure included a total of seven attention checks, each embedded within a different questionnaire. For example, the MINT questionnaire included an item such as: *"I can always accurately answer to the extreme left on this question to show that I am reading it."*

@@

The scale includes both high-level interoceptive dimensions - such as Body Listening, Noticing, and Emotional Awareness - and low-level dimensions, including Attention Regulation, Trust, and Self-Regulation [**ref**]. It also features dimensions whose relationship to interoception remains debated, and which tend to show weak or non-existent correlations with the other MAIA subscales -namely, Not-Distracting and Not-Worrying [@ferentzi2021examining].
